
\chapternonum{Liste des publications personnelles}

\section*{Articles parus}

\begin{itemize}
\item \textbf{Rocabert, C.}, Knibbe, C., Consuegra, J., Schneider, D., \& Beslon, G. (2017). Beware batch culture: Seasonality and niche construction predicted to favor bacterial adaptive diversification. \textit{PLoS Computational Biology}, 13(3), e1005459.
\item \textbf{Rocabert, C.}, Knibbe, C., \& Beslon, G. (2015, July). Towards a Integrated Evolutionary Model to Study Evolution of Evolution. In Proceedings of \textit{the First EvoEvo Workshop (Satellite workshop of ECAL 2015)} (York, UK).
\end{itemize}

\section*{Articles soumis ou en pr\'eparation}
\begin{itemize}
\item \textbf{Rocabert, C.}, Bernard, S., Beslon, G., \& Knibbe, C. (2017). Phenotypic Noise and the Cost of Complexity. \textit{Evolution}, under review.
\item Gippet M.W., J., \textbf{Rocabert, C.}, Fenet, S., \& Kaufmann, B. MoRIS: Model of Routes of Invasive Spread. Human-mediated dispersal, road network and invasion parameters. In preparation.
\end{itemize}

\section*{Résumés des conférences}
\begin{itemize}
\item \textbf{Rocabert, C.}, Knibbe C., Consuegra J., Schneider D., \& Beslon G. (2017, September) Environmental seasonality drives digital populations towards stable cross-feeding. In Proceedings of \textit{ECAL 2017 conference. 14\textsuperscript{th} European Conference on Artificial Life} (Lyon, France). Communication orale
\item \textbf{Rocabert, C.}, Knibbe, C., Consuegra, J., Schneider, D., \& Beslon, G. (2016, September). In Silico Experimental Evolution Highlights the Influence of Environmental Seasonality on Bacterial Diversification. In Proceedings of \textit{the Second EvoEvo Workshop. Satellite workshop of CCS2016} (Amsterdam, Netherlands). Communication orale
\item Gippet, J., Fenet, S., Dumet, A., Kaufmann, B. \& \textbf{Rocabert, C.} (2016, August) MoRIS: Model of Routes of Invasive Spread. Human-mediated dispersal, road network and invasion parameters. In Proceedings of \textit{IENE 2016 conference. 5\textsuperscript{th} International Conference on Ecology and Transportation: Integrating Transport Infrastructures with Living Landscapes} (Lyon, France). Communication orale par J. Gippet.
\item \textbf{Rocabert, C.}, Knibbe, C., Consuegra, J., Schneider, D. \& Beslon, G. (2016, April). In Silico Experimental Evolution Highlights the Influence of Environmental Seasonality on Bacterial Diversification. In \textit{EvoAct: Evolution in action with living and artificial organisms conference} (Autrans, France). Communication orale
\item \textbf{Rocabert, C.}, Knibbe C., Consuegra J., Schneider D., \& Beslon G. (2016, March) Environmental Driving of Bacterial Diversification in In Silico Experimental Evolution. In \textit{Evolutionary systems biology: from model organisms to human disease workshop}, (Cambridge, UK). Poster
\item Gippet, J., \textbf{Rocabert, C.}, Fenet, S., Dumet, A., \& Kaufmann, B. (2015, July). Modeling and evaluating human-mediated dispersal mechanisms at landscape scale: a study of road network and invasion parameters for Lasius neglectus ants invasive species. In Proceedings of \textit{World Conference on Natural Resource Modeling} (Bordeaux, France). Communication orale par J. Gippet.
\end{itemize}
